Rationality, Evolution \& the Environment

### 2015-08-20 paper/paper.tex
fixed tables; edits results section; added extensions section

\section{Results}

In this section we develop results by means of computer simulations and analytical proofs in parallel.

\subsection{Statics}

Table \ref{tab:reg vs obj} represent the result of simulations over $50.000$ games in $\mathcal{G}$ with $a,b,c,d \in \lbrace  0, \dots, 10 \rbrace$. The number in each cell corresponds to the average evolutionary fitness of the row player when matched with the column player.

\begin{table}[]
\centering
\caption{Average evolutionary fitness in simulations of 50.000 symmetric $2 \times 2$ games}
\label{tab:reg vs obj}
\begin{tabular}{cccll}
\cline{1-3}
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{$\tau^{\pi}, \Delta(A_{-i})$} & \multicolumn{1}{c|}{$\tau^{reg}, \Delta(A_{-i})$} &  &  \\ \cline{1-3}
\multicolumn{1}{|c|}{$\tau^{\pi}, \Delta(A_{-i})$} & \multicolumn{1}{c|}{6.131} & \multicolumn{1}{c|}{6.128} &  &  \\ \cline{1-3}
\multicolumn{1}{|c|}{$\tau^{reg}, \Delta(A_{-i})$} & \multicolumn{1}{c|}{6.305} & \multicolumn{1}{c|}{6.302} &  &  \\ \cline{1-3}
\multicolumn{1}{l}{}   & \multicolumn{1}{l}{}  & \multicolumn{1}{l}{}  &  & 
\end{tabular}
\end{table}

Table \ref{tab:reg vs obj} shows that when players in the population are radically uncertain ($\Delta(A_{-i})$), the regret player $ \tau^{reg} $ outperforms the objective type $  \tau^{\pi} $, and $ \tau^{reg} $  is evolutionarily stable whereas $ \tau^{\pi} $ is not. This suggests that in the presence of uncertainty, in the sense of a set of probability measures, regret minimization is a better choice rule as compared with standard maxmin from an evolutionary point of view. \\
\noindent Table \ref{tab:reg vs obj 2} reproduces the results about average evolutionary fitness out of 5.000 randomly generated symmetric $2 \times 2$ games when both types of epistemic uncertainty are present in the population. As we already highlighted in Fact \ref{fact:equivalence2x2}, $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$, and $(\tau^{\pi}, \overline{\mu})$ are behaviorally equivalent, and their evolutionary fitness is indeed the same. [WARNING: it is not exactly identical here, this is probably related to a difference in tie-breaking that is probably a bit different for player $\tau^{reg}, \Delta(A_{-i})$. VERIFY and EQUALIZE.]\\
Consequently, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$, and $(\tau^{\pi}, \overline{\mu})$ are neutrally stable, and again $(\tau^{\pi}, \Delta(A_{-i}))$ is not.

\begin{table*}[ht]
\centering
\begin{tabular}{ccccc}
  \hline
 & $\tau^{reg}, \Delta(A_{-i})$ 
 & $\tau^{\pi}, \Delta(A_{-i})$ 
 & $\tau^{reg}, \overline{\mu}$ 
 & $\tau^{\pi}, \overline{\mu}$ \\ 
  \hline
  $\tau^{reg}, \Delta(A_{-i})$ & 6.629 & 6.653 &  6.636 & 6.636  \\ 
  $\tau^{\pi}, \Delta(A_{-i})$  & 6.455 & 6.468 & 6.462 & 6.462  \\ 
  $\tau^{reg}, \overline{\mu}$ & 6.633 & 6.658 & 6.634 & 6.634  \\ 
  $\tau^{\pi}, \overline{\mu}$ & 6.633 & 6.658 & 6.634 & 6.634  \\   
   \hline
\end{tabular}
\caption{Average evolutionary fitness in simulations of 5000 symmetric $2 \times 2$ games}
\label{tab:reg vs obj 2}
\end{table*}

On the top of what we have seen so far, we can proceed with the main analytical results of the paper, which confirm our achievements from simulations. Let us call $\Lambda$ the set of possible players $( \tau, e  )$ in the population. We can now state the following proposition.

@@

Fix $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})) \rbrace$ and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d. values. Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only evolutionarily stable player in the population.

@@

Fix $T = \lbrace \tau^{\pi}, \tau^{reg} \rbrace$, $E = \lbrace \Delta(A_{-i}), \overline{\mu}  \rbrace$, $\Lambda= T \times E$, and $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex, set of i.i.d. values. Then, players $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ are neutrally stable, and $(\tau^{\pi}, \Delta(A_{-i}))$ is neither evolutionarily nor neutrally stable.

@@

\subsection{More types}

@@

\begin{table*}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
 & $\tau^{reg}, \Delta(A_{-i})$ 
 & $\tau^{\pi}, \Delta(A_{-i})$ 
 & $\tau^{alt}, \Delta(A_{-i})$
 & $\tau^{com}, \Delta(A_{-i})$ \\ 
  \hline
  $\tau^{reg}, \Delta(A_{-i})$ & 6.629 & 6.653 & 5.806 & 7.089  \\ 
  $\tau^{\pi}, \Delta(A_{-i})$  & 6.455 & 6.468 & 6.067 & 6.685  \\ 
  $\tau^{alt}, \Delta(A_{-i})$ & 6.280 & 6.746 & 5.473 & 6.959 \\ 
  $\tau^{com}, \Delta(A_{-i})$ & 5.936 & 5.735 & 5.336 & 6.379  \\ 
   \hline
\end{tabular}
\caption{Average evolutionary fitness in simulations of 5000 symmetric $2 \times 2$ games}
\label{tab:Utils-MetaGame}
\end{table*}

@@

Finally, Table \ref{tab:Utils-MetaGame2} shows the average fitness when all the epistemic and player types introduced so far are simultaneously present in the population. [SAME WARNING: it is not exactly identical here, this is probably related to a difference in tie-breaking that is probably a bit different for player $\tau^{reg}, \Delta(A_{-i})$. VERIFY and EQUALIZE.]\\
A monomorphic population of regret
minimizers $\tuple{\tuple{\tau^{reg}, \Delta(A)}}$ is no longer
evolutionarily stable: it could be invaded by expected utility maximizers of types $\tuple{\tau^{reg}, \bar{\mu}}$ and $\tuple{\tau^{\pi},
  \bar{\mu}}$. Since the latter are behaviorally equivalent, neither
is an evolutionarily stable strategy, but could at best be
\emph{neutrally stable}
\cite{Maynard-Smith1982:Evolution-and-t}. However, under our simulated
meta-game payoffs from Table~\ref{tab:Utils-MetaGame2} any population
consisting entirely of $\tuple{\tau^{reg}, \bar{\mu}}$ and
$\tuple{\tau^{\pi}, \bar{\mu}}$ can be invaded by regret
minimizers. This suggests that all three types would persist under
standard evolutionary dynamics, in various relative proportions.

Simulation results of the (discrete time) \emph{replicator dynamics}
\cite{TaylorJonker1978:Evolutionary-St} indeed show that random
initial population configurations are attracted to states with only
three player types: $\tuple{\tau^{reg}, \Delta(A)}$,
$\tuple{\tau^{reg}, \bar{\mu}}$ and $\tuple{\tau^{\pi},
  \bar{\mu}}$. The relative proportions of these depend on the initial
population. This variability is eradicated if we add a small mutation
rate to the dynamics. We assume a fixed, small mutation rate
$\epsilon$ for the probability that a player's preference type
\emph{or} her epistemic type changes to another random preference type
or epistemic type. The probability that a player type randomly mutates
into a completely different player type with altogether different
preference type and epistemic type would then be $\epsilon^2$. With
these assumptions about ``local mutations'', numerical simulations of
the (discrete time) \emph{replicator mutator dynamics}
\cite{Nowak2006:Evolutionary-Dy} show that for very small
mutation rates almost all initial populations converge to a single
fixed point in which the majority of players are regret types. For
instance, with $\epsilon = 0.001$, almost all initial populations are
attracted to a final distribution with proportions:

@@

\begin{table*}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
 & $\tuple{\tau^{reg}, \Delta(A)}$ 
 & $\tuple{\tau^{\pi}, \Delta(A)}$ 
 & $\tuple{\tau^{alt}, \Delta(A)}$
 & $\tuple{\tau^{com}, \Delta(A)}$
 & $\tuple{\tau^{reg}, \bar{\mu}}$ 
 & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
 & $\tuple{\tau^{alt}, \bar{\mu}}$
 & $\tuple{\tau^{com}, \bar{\mu}}$ \\ 
  \hline
  $\tuple{\tau^{reg}, \Delta(A)}$ & 6.629 & 6.653 & 5.806 & 7.089 & 6.636 & 6.636 & 5.793 & 7.463 \\ 
  $\tuple{\tau^{\pi}, \Delta(A)}$  & 6.455 & 6.468 & 6.067 & 6.685 & 6.462 & 6.462 & 6.065 & 6.834 \\ 
  $\tuple{\tau^{alt}, \Delta(A)}$ & 6.280 & 6.746 & 5.473 & 6.959 & 6.294 & 6.294 & 5.474 & 7.114 \\ 
  $\tuple{\tau^{com}, \Delta(A)}$ & 5.936 & 5.735 & 5.336 & 6.379 & 5.929 & 5.929 & 5.327 & 6.538 \\ 
  $\tuple{\tau^{reg}, \bar{\mu}}$ & 6.633 & 6.658 & 5.810 & 7.081 & 6.634 & 6.634 & 5.802 & 7.454 \\ 
  $\tuple{\tau^{\pi}, \bar{\mu}}$ & 6.633 & 6.658 & 5.810 & 7.081 & 6.634 & 6.634 & 5.802 & 7.454 \\ 
  $\tuple{\tau^{alt}, \bar{\mu}}$ & 6.278 & 6.750 & 5.476 & 6.953 & 6.293 & 6.293 & 5.484 & 7.112 \\ 
  $\tuple{\tau^{com}, \bar{\mu}}$ & 6.311 & 5.885 & 5.475 & 6.536 & 6.299 & 6.299 & 5.466 & 7.123 \\ 
   \hline
\end{tabular}
\caption{Average fitness in simulations of 5000
  randomly generated $2 \times 2$ symmetric games.}
\label{tab:Utils-MetaGame2}
\end{table*}

\subsection{Symmetric $n \times n$ games}

...

\subsection{Dynamics}

ADD RESULTS FOR DYNAMICS

\subsection{Choice principles}

\begin{itemize}
\item study evolutionary competition between \emph{choice principles} 
\item for now a choice principle is a pair (epistemic type, preference type)
  \begin{itemize}
  \item two epistemic types:
    \begin{enumerate}
    \item probabilistic beliefs (assumed to be flat)
    \item non-probabilistic beliefs
    \end{enumerate}
  \item two preferences types (references to ``evolution of preference'' literature):
    \begin{enumerate}
    \item veridical payoff representations
    \item regret-based payoffs
    \end{enumerate}
  \item many other types are conceivable; more in discussion section
    \begin{itemize}
    \item we want to keep it simple
    \item assume that agents are relatively simple as well
    \item no learning from past encounters \& no reasoning about the opponent: agents simply do
      not know that there is another player (no strategic thinking possible; in line with idea
      of evolutionary game theory where agents are ``stupid'' and ``myopic'') \\
      \textcolor{blue}{this is then the added assumption that may be crude and generally
        implausible but allows us to deflect the economists' critique}
    \end{itemize}
  \item choice principles yield action choices for each game
    \begin{itemize}
    \item show how
    \end{itemize}
  \item RESULT: types (prob., veridical) and (prob., regret) are choice-equivalent (also
    mentioned by \citet{HalpernPass2012:Iterated-Regret})
  \item RESULT: in $2 \times 2$ cases, (prob., veridical), (prob., regret) and (non-prob.,
    regret) are choice-equivalent (but not for $n \times n$ in general)
    \begin{itemize}
    \item still we treat them as separate types because they behave differently under
      component-wise mutation (see below)
    \end{itemize}
  \end{itemize}
\end{itemize}

\subsection{Results}

\textcolor{gray}{keep this clean and concise, formal details (proofs) in appendix}

\subsubsection{$2 \times 2$ symmetric games}

\textcolor{gray}{we isolate this case because it is most basic, and we can offer analytical
  proofs as well}

\begin{itemize}
\item given previous results, there are really only two kinds of types to look at:
  \begin{enumerate}
  \item (prob., veridical), (prob., regret) and (non-prob., regret) \\ 
    \textcolor{gray}{[all choice-equivalent in this case]}
  \item (non-prob., veridical)
  \end{enumerate}
\item RESULT: the former class ``dominates'' the latter (our main result, Proposition 1 from
  TARK paper)
\item this means that evolutionary dynamics would weed out (non-prob., regret); every
  population composition between the remaining three is neutrally stable; all interior
  trajectories (of the replicator dynamic) converge to these
\item further results (from TARK):
  \begin{itemize}
  \item component-wise mutation: abundance of regret types
    \begin{itemize}
    \item different evolutionary paths despite the same behavior (contra the ``behavioral
      gambit'' \citep{FawcettHamblin2013:Exposing-the-be})
    \end{itemize}
  \item exogenously given correlated epistemic types: regret types dominate
  \item exogenously given uncorrelated epistemic types: regret types dominate
  \end{itemize}
\todo[inline]{work out these additional results more carefully; present graphs if possible}
\end{itemize}

\subsubsection{$n \times n$ symmetric games}

\todo[inline]{work out these additional results more carefully; present graphs if possible}

@@

\section*{APPENDIX: Proofs}

@@

\section*{Snippets}

>>>>

\section{Results: the basic model}

In this section we present results of computer simulations and analytical proofs for our basic
model with the four player types introduced in the previous section.

\subsection{Numerical simulations}

Table~\ref{tab:ExpectedFitness_4Types} gives an approximation of expected fitness, obtained
from averaging over randomly sampled $100,000$ games in $\mathcal{G}$ with
$a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$. The number in each cell corresponds to the average
evolutionary fitness of the row player when matched with the column player. Whenever a player
type would not select a unique action in a given game, we recorded unbiased averages over
playing either.

\begin{table}[t]
\centering
\begin{tabular}{ccccc}
  \toprule
 & $\tau^{reg}, \Delta(A_{-i})$ 
 & $\tau^{\pi}, \Delta(A_{-i})$ 
 & $\tau^{reg}, \overline{\mu}$ 
 & $\tau^{\pi}, \overline{\mu}$ \\ 
  \midrule
  $\tau^{reg}, \Delta(A_{-i})$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
  $\tau^{\pi}, \Delta(A_{-i})$ & 6.486 & 6.484 & 6.486 & 6.486 \\ 
  $\tau^{reg}, \overline{\mu}$ & 6.663 & 6.662 & 6.663 & 6.663 \\  
  $\tau^{\pi}, \overline{\mu}$ & 6.663 & 6.662 & 6.663 & 6.663 \\ 
   \bottomrule
\end{tabular}                    
\caption{Average evolutionary fitness in simulations of 100,000 symmetric $2 \times 2$ games}
\label{tab:ExpectedFitness_4Types}
\end{table}

Simulation results reflect Fact~\ref{fact:equivalence2x2} in that all encounters in which
types $\tau^{reg}, \Delta(A_{-i})$, $\tau^{reg}, \overline{\mu}$ or $\tau^{\pi},
\overline{\mu}$ are substituted for one another yield identical results. More interestingly,
Table~\ref{tab:ExpectedFitness_4Types} shows that the maximin strategy $\tau^{\pi},
\Delta(A_{-i})$ is strictly dominated by either of the three other strategies: in each row
column (i.e., for each kind of opponent), the maximin strategy is strictly worse than any of
the three behaviorally equivalent competitors. This has a number of interesting consequences.

Firstly, if we restrict attention to a population of radically uncertain players where only
epistemic type exists $\Delta(A_{-i})$, the regret type $ \tau^{reg} $ is the only
evolutionarily stable state; we expect selection that is driven by expected fitness to
invariably weed out maximin behavior in favor of regret minimization. In other words, in the
class of random games looked at here, regret minimization is a better choice rule than standard
maxmin from an evolutionary point of view.

Secondly, if we look at the competition between all four types represented in
Table~\ref{tab:ExpectedFitness_4Types}, $\tau^{reg}, \Delta(A_{-i})$ is no longer the only
evolutionarily stable type in this meta-game. Rather, given behavioral equivalence
(Fact~\ref{fact:equivalence2x2}), types $(\tau^{reg}, \Delta(A_{-i}))$,
$(\tau^{reg}, \overline{\mu})$, and $(\tau^{\pi}, \overline{\mu})$ are all neutrally stable
\citep{Maynard-Smith1982:Evolution-and-t}, while $(\tau^{\pi}, \Delta(A_{-i}))$ is strictly
dominated and so disfavored by fitness-based selection. Based on considerations of evolutionary
stability in this meta-game, we are drawn to conclude that maximin behavior is weeded out in
favor of a population with a random distribution of the remaining three types.

Simulation results of the (discrete time) \emph{replicator dynamics}
\citep{TaylorJonker1978:Evolutionary-St} indeed show that random initial population
configurations are attracted to states with only three player types:
$\tuple{\tau^{reg}, \Delta(A)}$, $\tuple{\tau^{reg}, \bar{\mu}}$ and
$\tuple{\tau^{\pi}, \bar{\mu}}$. The relative proportions of these depend on the initial
population.

Interestingly, however, this variability is eradicated if we add a small mutation rate to the
dynamics. We assume a fixed, small mutation rate $\epsilon$ for the probability that a player's
preference type \emph{or} her epistemic type changes to another random preference type or
epistemic type. The probability that a player type randomly mutates into a completely different
player type with altogether different preference type and epistemic type would then be
$\epsilon^2$. With these assumptions about ``local mutations'', numerical simulations of the
(discrete time) \emph{replicator mutator dynamics} \citep{Nowak2006:Evolutionary-Dy} show that
for very small mutation rates almost all initial populations converge to a single fixed point
in which the majority of players are regret types. For instance, with $\epsilon = 0.001$,
almost all initial populations are attracted to a final distribution with proportions:

What this suggests is that, since biological evolution selects behavior-generating mechanisms,
not behavior as such, it need not be the case that behaviorally equivalent mechanisms are
treated equally all the while. If mutation probabilities are a function of individual
components of such behavior-generating mechanisms, it can be the case that certain components
are more strongly favored by a process of random mutation and selection. This is exactly the
case with regret-based subjective preferences in our little toy example here. Since
regret-based subjective preferences are much better in connection with radical uncertainty than
veridical preferences are, we see a majority of regret-based preference types paired with
probabilistic epistemic types. In sum, component-wise mutation could have lead to a majority of
regret-based players even if they are behaviorally indiscernible from decision makers with
veridical preferences.

\subsection{Analytical results}
\label{sec:analytical-results}

Results based on the single meta-game in Table~\ref{tab:Utils-MetaGame}, which was obtained by
averaging over numerical simulations, are not fully general and possibly spoiled by random
fluctuations in the sampling procedure. Fortunately, for the case of symmetric $2 \times 2$
games, the main result that maximin types $(\tau^{\pi}, \Delta(A_{-i}))$ are strictly dominated
can also be shown analytically for generous general conditions on the nature of $P(G)$.

@@

  Let $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})) \rbrace$ be
  the set of possible players $(\tau, e)$ in the population, and let $\mathcal{G}$ be the class
  of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex,
  set of i.i.d.~values. Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only strict Nash
  equilibrium in the resulting meta-game.

@@

  Fix $T = \lbrace \tau^{\pi}, \tau^{reg} \rbrace$,
  $E = \lbrace \Delta(A_{-i}), \overline{\mu} \rbrace$, $\Lambda= T \times E$, and
  $\mathcal{G}$ the class of symmetric $2 \times 2$ games with payoffs sampled from a finite,
  or compact and convex, set of i.i.d. values. Then, player type $(\tau^{\pi}, \Delta(A_{-i}))$
  is strictly dominated by $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
  $(\tau^{reg}, \overline{\mu})$.

@@

Corollary~\ref{corollary1} tells us that the results obtained for the meta-game in
Table~\ref{tab:Utils-MetaGame} hold more generally for any class of games in which the
probability of encountering a game is the product of independently sampling four identically
distributed payoff values. As before, player types $(\tau^{reg}, \Delta(A_{-i}))$,
$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ will be neutrally stable,
and fitness-based selection will tend to weed out maximin-players and leave us with a
population of arbitrary frequency of $(\tau^{reg}, \Delta(A_{-i}))$,
$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ players.

\section{Extensions}
\label{sec:extensions}

The basic results from the previous section demonstrate the main conceptual point that we
wanted to make: non-veridical subjective preference relations can persist under evolutionary
selection along a gradient of objective fitness. In particular, regret-based preferences can
not only persist, but even be favored by natural selection if agents are radically
uncertain. This holds generally for playing arbitrary $2 \times 2$ games whose payoffs are
sampled identically and independently at random.

How do the basic results from the previous section carry over to more encompassing, richer
models? Section~\ref{sec:more-types} first considers a further conceptually interesting
preference types that have been suggested in the recent literature. Section~XZY then looks at
the basic cast of player types, but considers the case of $n \times n$ games. Finally, to put
our results into the proper perspective, Section~XZY ends with a brief comparison of game
situations with cases of solitary decision making.

\subsection{More types}
\label{sec:more-types}

@@

\begin{table*}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
 & $\tau^{reg}, \Delta(A_{-i})$ 
 & $\tau^{\pi}, \Delta(A_{-i})$ 
 & $\tau^{com}, \Delta(A_{-i})$
 & $\tau^{alt}, \Delta(A_{-i})$ \\ 
  \hline
  $\tau^{reg}, \Delta(A_{-i})$ & 6.663 & 6.662 & 5.829 & 7.105 \\ 
  $\tau^{\pi}, \Delta(A_{-i})$ & 6.486 & 6.484 & 6.088 & 6.703 \\ 
  $\tau^{com}, \Delta(A_{-i})$ & 6.323 & 6.758 & 5.496 & 6.977 \\ 
  $\tau^{alt}, \Delta(A_{-i})$ & 5.949 & 5.722 & 5.326 & 6.396 \\ 
   \hline
\end{tabular}
\caption{Average payoff in simulations of 100,000 symmetric $2 \times 2$ games}
\label{tab:Utils-MetaGame}
\end{table*}

@@

Finally, Table \ref{tab:Utils-MetaGame2} shows the average fitness when all the epistemic and
player types introduced so far are simultaneously present in the population.

@@

\begin{table*}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
 & $\tuple{\tau^{reg}, \Delta(A)}$ 
 & $\tuple{\tau^{\pi}, \Delta(A)}$ 
 & $\tuple{\tau^{com}, \Delta(A)}$
 & $\tuple{\tau^{alt}, \Delta(A)}$
 & $\tuple{\tau^{reg}, \bar{\mu}}$ 
 & $\tuple{\tau^{\pi}, \bar{\mu}}$ 
 & $\tuple{\tau^{com}, \bar{\mu}}$
 & $\tuple{\tau^{alt}, \bar{\mu}}$ \\ 
  \hline
  $\tuple{\tau^{reg}, \Delta(A)}$ &  6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\  
  $\tuple{\tau^{\pi}, \Delta(A)}$ &  6.486 & 6.484 & 6.088 & 6.703 & 6.486 & 6.486 & 6.088 & 6.875 \\  
  $\tuple{\tau^{com}, \Delta(A)}$ &  6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\  
  $\tuple{\tau^{alt}, \Delta(A)}$ &  5.949 & 5.722 & 5.326 & 6.396 & 5.949 & 5.949 & 5.326 & 6.568 \\  
  $\tuple{\tau^{reg}, \bar{\mu}}$ &  6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\  
  $\tuple{\tau^{\pi}, \bar{\mu}}$ &  6.663 & 6.662 & 5.829 & 7.105 & 6.663 & 6.663 & 5.829 & 7.489 \\  
  $\tuple{\tau^{com}, \bar{\mu}}$ &  6.323 & 6.758 & 5.496 & 6.977 & 6.323 & 6.323 & 5.496 & 7.149 \\  
  $\tuple{\tau^{alt}, \bar{\mu}}$ &  6.331 & 5.893 & 5.497 & 6.566 & 6.331 & 6.331 & 5.497 & 7.152 \\   
   \hline                          
\end{tabular}                      
\caption{Average payoff in simulations of 100,000
  randomly generated $2 \times 2$ symmetric games.}
\label{tab:Utils-MetaGame2}        
\end{table*}

\subsection{$n \times n$ symmetric games}
\label{sec:n-times-n}

\subsection{Solitary decisions}
\label{sec:solitary-decisions}

@@

\appendix

\section{Proofs}

@@

\section{Snippets}
